### 2020-10-17 forward_corr.tex
done

% Created by tikzDevice version 0.12.3 on 2020-09-28 00:14:35
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
	( 49.28,444.83) --
	( 57.86,444.83) --
	( 66.44,445.43) --
	( 75.02,445.66) --
	( 83.60,446.22) --
	( 92.18,446.31) --
	(100.76,447.61) --
	(109.34,447.61) --
	(117.92,448.49) --
	(126.50,449.19) --
	(135.08,450.49) --
	(143.66,451.74) --
	(152.24,454.24) --
	(160.82,455.12) --
	(169.40,458.60) --
	(177.98,460.51) --
	(186.56,463.75) --
	(195.14,469.23) --
	(203.72,472.61) --
	(212.30,477.86) --
	(220.88,481.80) --
	(229.46,489.82) --
	(238.04,497.94) --
	(246.62,502.53) --
	(255.20,508.10) --
	(263.78,517.98) --
	(272.36,523.55) --
	(280.94,528.79) --
	(289.52,534.22) --
	(298.10,533.76) --
	(306.68,535.43) --
	(315.26,531.67) --
	(323.84,527.31) --
	(332.42,522.81) --
	(341.00,515.11) --
	(349.58,506.34) --
	(358.16,499.06) --
	(366.74,490.57) --
	(375.32,481.01) --
	(383.90,474.65) --
	(392.48,471.50) --
	(401.06,463.52) --
	(409.64,462.18) --
	(418.22,456.66) --
	(426.80,454.47) --
	(435.38,452.02) --
	(443.96,450.86) --
	(452.54,449.28) --
	(461.12,448.63) --
	(469.70,447.61) --
	(478.28,446.68) --
	(486.86,445.61) --
	(495.44,445.89) --
	(504.02,445.15) --
	(512.60,444.87) --
	(521.18,444.55) --
	(529.76,444.50) --
	(538.34,444.36) --
	(546.92,444.13) --
	(555.50,444.22) --
	(564.08,444.08) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.73) --
	( 57.86,444.92) --
	( 66.44,444.92) --
	( 75.02,444.96) --
	( 83.60,445.71) --
	( 92.18,446.68) --
	(100.76,445.85) --
	(109.34,447.19) --
	(117.92,447.52) --
	(126.50,448.72) --
	(135.08,449.14) --
	(143.66,449.79) --
	(152.24,451.41) --
	(160.82,453.64) --
	(169.40,455.17) --
	(177.98,458.28) --
	(186.56,459.44) --
	(195.14,462.45) --
	(203.72,467.93) --
	(212.30,471.41) --
	(220.88,478.46) --
	(229.46,479.53) --
	(238.04,488.11) --
	(246.62,497.48) --
	(255.20,501.28) --
	(263.78,507.22) --
	(272.36,516.82) --
	(280.94,521.69) --
	(289.52,526.84) --
	(298.10,534.27) --
	(306.68,533.80) --
	(315.26,534.22) --
	(323.84,531.53) --
	(332.42,529.67) --
	(341.00,522.16) --
	(349.58,514.60) --
	(358.16,508.15) --
	(366.74,500.45) --
	(375.32,493.03) --
	(383.90,479.80) --
	(392.48,475.16) --
	(401.06,472.94) --
	(409.64,463.98) --
	(418.22,462.55) --
	(426.80,458.60) --
	(435.38,455.54) --
	(443.96,452.99) --
	(452.54,451.51) --
	(461.12,449.65) --
	(469.70,448.30) --
	(478.28,448.03) --
	(486.86,447.47) --
	(495.44,446.36) --
	(504.02,445.20) --
	(512.60,445.61) --
	(521.18,444.92) --
	(529.76,444.69) --
	(538.34,444.87) --
	(546.92,444.22) --
	(555.50,444.22) --
	(564.08,444.22) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
	( 49.28,444.59) --
	( 57.86,444.87) --
	( 66.44,444.87) --
	( 75.02,444.92) --
	( 83.60,445.48) --
	( 92.18,446.26) --
	(100.76,445.85) --
	(109.34,446.77) --
	(117.92,447.38) --
	(126.50,448.91) --
	(135.08,448.86) --
	(143.66,449.74) --
	(152.24,450.67) --
	(160.82,451.97) --
	(169.40,455.68) --
	(177.98,456.98) --
	(186.56,459.21) --
	(195.14,461.57) --
	(203.72,466.81) --
	(212.30,469.97) --
	(220.88,475.30) --
	(229.46,480.13) --
	(238.04,486.11) --
	(246.62,494.09) --
	(255.20,499.75) --
	(263.78,504.90) --
	(272.36,514.92) --
	(280.94,519.79) --
	(289.52,525.64) --
	(298.10,533.43) --
	(306.68,530.37) --
	(315.26,535.47) --
	(323.84,535.52) --
	(332.42,528.79) --
	(341.00,524.29) --
	(349.58,518.26) --
	(358.16,510.98) --
	(366.74,502.95) --
	(375.32,492.24) --
	(383.90,485.97) --
	(392.48,475.16) --
	(401.06,471.04) --
	(409.64,468.58) --
	(418.22,464.03) --
	(426.80,458.19) --
	(435.38,456.47) --
	(443.96,453.59) --
	(452.54,451.69) --
	(461.12,449.93) --
	(469.70,448.86) --
	(478.28,447.38) --
	(486.86,447.38) --
	(495.44,446.31) --
	(504.02,445.52) --
	(512.60,445.89) --
	(521.18,444.78) --
	(529.76,444.92) --
	(538.34,444.73) --
	(546.92,444.45) --
	(555.50,444.55) --
	(564.08,444.22) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
	( 49.28,445.29) --
	( 57.86,444.73) --
	( 66.44,445.52) --
	( 75.02,445.71) --
	( 83.60,445.94) --
	( 92.18,446.54) --
	(100.76,447.19) --
	(109.34,448.44) --
	(117.92,448.49) --
	(126.50,449.60) --
	(135.08,450.39) --
	(143.66,451.32) --
	(152.24,453.78) --
	(160.82,456.89) --
	(169.40,458.56) --
	(177.98,461.06) --
	(186.56,464.08) --
	(195.14,467.79) --
	(203.72,472.85) --
	(212.30,479.62) --
	(220.88,482.40) --
	(229.46,491.59) --
	(238.04,496.88) --
	(246.62,500.63) --
	(255.20,511.67) --
	(263.78,517.61) --
	(272.36,521.51) --
	(280.94,527.91) --
	(289.52,532.83) --
	(298.10,533.94) --
	(306.68,534.73) --
	(315.26,530.42) --
	(323.84,527.91) --
	(332.42,524.11) --
	(341.00,513.39) --
	(349.58,508.89) --
	(358.16,496.69) --
	(366.74,489.92) --
	(375.32,482.45) --
	(383.90,471.78) --
	(392.48,470.99) --
	(401.06,464.40) --
	(409.64,460.04) --
	(418.22,456.10) --
	(426.80,454.66) --
	(435.38,452.62) --
	(443.96,450.35) --
	(452.54,449.19) --
	(461.12,448.21) --
	(469.70,446.73) --
	(478.28,446.82) --
	(486.86,445.99) --
	(495.44,445.61) --
	(504.02,445.01) --
	(512.60,445.01) --
	(521.18,444.87) --
	(529.76,444.64) --
	(538.34,444.50) --
	(546.92,444.27) --
	(555.50,444.04) --
	(564.08,444.18) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
	( 49.28,444.64) --
	( 57.86,444.83) --
	( 66.44,444.96) --
	( 75.02,445.24) --
	( 83.60,445.52) --
	( 92.18,446.03) --
	(100.76,445.85) --
	(109.34,447.52) --
	(117.92,447.70) --
	(126.50,448.72) --
	(135.08,448.72) --
	(143.66,450.95) --
	(152.24,450.72) --
	(160.82,453.41) --
	(169.40,455.12) --
	(177.98,457.86) --
	(186.56,461.20) --
	(195.14,463.24) --
	(203.72,465.70) --
	(212.30,470.25) --
	(220.88,478.55) --
	(229.46,483.05) --
	(238.04,487.83) --
	(246.62,496.09) --
	(255.20,498.78) --
	(263.78,507.68) --
	(272.36,517.98) --
	(280.94,520.07) --
	(289.52,524.38) --
	(298.10,531.39) --
	(306.68,534.13) --
	(315.26,534.27) --
	(323.84,531.67) --
	(332.42,528.65) --
	(341.00,526.29) --
	(349.58,513.62) --
	(358.16,507.31) --
	(366.74,502.02) --
	(375.32,490.57) --
	(383.90,484.35) --
	(392.48,477.02) --
	(401.06,473.22) --
	(409.64,465.52) --
	(418.22,460.97) --
	(426.80,458.37) --
	(435.38,454.89) --
	(443.96,452.85) --
	(452.54,451.32) --
	(461.12,448.63) --
	(469.70,448.58) --
	(478.28,447.42) --
	(486.86,446.68) --
	(495.44,446.31) --
	(504.02,445.75) --
	(512.60,445.29) --
	(521.18,445.15) --
	(529.76,444.64) --
	(538.34,444.32) --
	(546.92,444.50) --
	(555.50,444.41) --
	(564.08,444.36) --
	(572.66,444.22);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
	( 49.28,444.73) --
	( 57.86,444.83) --
	( 66.44,445.29) --
	( 75.02,445.10) --
	( 83.60,445.43) --
	( 92.18,446.08) --
	(100.76,446.54) --
	(109.34,446.82) --
	(117.92,448.26) --
	(126.50,448.63) --
	(135.08,449.42) --
	(143.66,450.44) --
	(152.24,451.92) --
	(160.82,454.38) --
	(169.40,456.28) --
	(177.98,457.21) --
	(186.56,461.43) --
	(195.14,465.10) --
	(203.72,468.62) --
	(212.30,472.06) --
	(220.88,476.60) --
	(229.46,482.68) --
	(238.04,491.35) --
	(246.62,496.64) --
	(255.20,505.78) --
	(263.78,511.49) --
	(272.36,516.17) --
	(280.94,525.50) --
	(289.52,528.14) --
	(298.10,530.69) --
	(306.68,535.15) --
	(315.26,535.66) --
	(323.84,530.42) --
	(332.42,526.05) --
	(341.00,520.02) --
	(349.58,514.46) --
	(358.16,504.16) --
	(366.74,498.50) --
	(375.32,490.84) --
	(383.90,481.06) --
	(392.48,474.24) --
	(401.06,468.35) --
	(409.64,466.49) --
	(418.22,461.11) --
	(426.80,456.70) --
	(435.38,454.34) --
	(443.96,452.67) --
	(452.54,451.92) --
	(461.12,449.74) --
	(469.70,448.21) --
	(478.28,447.28) --
	(486.86,447.01) --
	(495.44,445.71) --
	(504.02,445.52) --
	(512.60,445.20) --
	(521.18,445.34) --
	(529.76,444.55) --
	(538.34,444.41) --
	(546.92,444.18) --
	(555.50,444.13) --
	(564.08,444.27) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
	( 49.28,444.83) --
	( 57.86,445.20) --
	( 66.44,444.96) --
	( 75.02,445.61) --
	( 83.60,445.75) --
	( 92.18,446.59) --
	(100.76,446.91) --
	(109.34,447.79) --
	(117.92,447.93) --
	(126.50,449.65) --
	(135.08,450.53) --
	(143.66,451.13) --
	(152.24,454.38) --
	(160.82,454.80) --
	(169.40,458.70) --
	(177.98,460.32) --
	(186.56,462.87) --
	(195.14,467.37) --
	(203.72,472.06) --
	(212.30,476.60) --
	(220.88,480.13) --
	(229.46,489.04) --
	(238.04,495.25) --
	(246.62,502.53) --
	(255.20,509.35) --
	(263.78,515.52) --
	(272.36,523.60) --
	(280.94,528.37) --
	(289.52,530.23) --
	(298.10,534.64) --
	(306.68,537.42) --
	(315.26,530.55) --
	(323.84,529.86) --
	(332.42,520.72) --
	(341.00,515.20) --
	(349.58,504.21) --
	(358.16,501.47) --
	(366.74,492.33) --
	(375.32,480.92) --
	(383.90,476.88) --
	(392.48,471.45) --
	(401.06,463.98) --
	(409.64,462.41) --
	(418.22,457.68) --
	(426.80,454.52) --
	(435.38,453.59) --
	(443.96,452.02) --
	(452.54,451.13) --
	(461.12,447.79) --
	(469.70,447.33) --
	(478.28,446.91) --
	(486.86,446.22) --
	(495.44,445.48) --
	(504.02,445.34) --
	(512.60,445.15) --
	(521.18,444.55) --
	(529.76,444.69) --
	(538.34,444.45) --
	(546.92,444.22) --
	(555.50,444.13) --
	(564.08,444.13) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,444.64) --
	( 57.86,445.15) --
	( 66.44,445.15) --
	( 75.02,445.29) --
	( 83.60,446.03) --
	( 92.18,446.12) --
	(100.76,447.05) --
	(109.34,447.79) --
	(117.92,447.61) --
	(126.50,449.05) --
	(135.08,450.07) --
	(143.66,450.76) --
	(152.24,453.32) --
	(160.82,455.03) --
	(169.40,457.95) --
	(177.98,459.07) --
	(186.56,462.04) --
	(195.14,466.58) --
	(203.72,469.83) --
	(212.30,475.16) --
	(220.88,479.90) --
	(229.46,485.28) --
	(238.04,494.51) --
	(246.62,499.52) --
	(255.20,510.70) --
	(263.78,510.89) --
	(272.36,521.93) --
	(280.94,525.73) --
	(289.52,530.42) --
	(298.10,534.08) --
	(306.68,534.96) --
	(315.26,533.43) --
	(323.84,529.77) --
	(332.42,525.87) --
	(341.00,516.45) --
	(349.58,507.31) --
	(358.16,501.98) --
	(366.74,494.79) --
	(375.32,484.58) --
	(383.90,480.27) --
	(392.48,470.80) --
	(401.06,468.30) --
	(409.64,462.08) --
	(418.22,458.28) --
	(426.80,456.79) --
	(435.38,452.94) --
	(443.96,452.34) --
	(452.54,450.81) --
	(461.12,448.86) --
	(469.70,447.79) --
	(478.28,447.01) --
	(486.86,446.73) --
	(495.44,445.38) --
	(504.02,446.08) --
	(512.60,445.15) --
	(521.18,444.92) --
	(529.76,444.41) --
	(538.34,444.45) --
	(546.92,444.45) --
	(555.50,444.45) --
	(564.08,444.55) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.27) --
	( 49.28,444.73) --
	( 57.86,444.96) --
	( 66.44,445.34) --
	( 75.02,445.06) --
	( 83.60,445.85) --
	( 92.18,446.12) --
	(100.76,447.01) --
	(109.34,447.28) --
	(117.92,447.61) --
	(126.50,449.05) --
	(135.08,449.46) --
	(143.66,450.81) --
	(152.24,452.29) --
	(160.82,455.31) --
	(169.40,455.87) --
	(177.98,459.67) --
	(186.56,461.20) --
	(195.14,466.17) --
	(203.72,468.44) --
	(212.30,473.36) --
	(220.88,478.74) --
	(229.46,485.65) --
	(238.04,492.05) --
	(246.62,498.08) --
	(255.20,507.96) --
	(263.78,512.32) --
	(272.36,521.74) --
	(280.94,525.87) --
	(289.52,529.21) --
	(298.10,535.19) --
	(306.68,534.17) --
	(315.26,536.63) --
	(323.84,529.39) --
	(332.42,526.24) --
	(341.00,518.03) --
	(349.58,511.63) --
	(358.16,502.77) --
	(366.74,497.76) --
	(375.32,484.40) --
	(383.90,479.57) --
	(392.48,472.47) --
	(401.06,469.51) --
	(409.64,463.20) --
	(418.22,458.05) --
	(426.80,456.24) --
	(435.38,453.22) --
	(443.96,451.97) --
	(452.54,449.70) --
	(461.12,449.51) --
	(469.70,448.03) --
	(478.28,447.28) --
	(486.86,446.91) --
	(495.44,445.43) --
	(504.02,445.94) --
	(512.60,445.24) --
	(521.18,444.92) --
	(529.76,444.22) --
	(538.34,444.50) --
	(546.92,444.55) --
	(555.50,444.36) --
	(564.08,444.36) --
	(572.66,444.27);
\definecolor{drawColor}{RGB}{253,231,37}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-10-16 22:00:47
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
	( 49.28,444.83) --
	( 57.86,444.83) --
	( 66.44,445.43) --
	( 75.02,445.66) --
	( 83.60,446.22) --
	( 92.18,446.31) --
	(100.76,447.61) --
	(109.34,447.61) --
	(117.92,448.49) --
	(126.50,449.19) --
	(135.08,450.49) --
	(143.66,451.74) --
	(152.24,454.24) --
	(160.82,455.12) --
	(169.40,458.60) --
	(177.98,460.51) --
	(186.56,463.75) --
	(195.14,469.23) --
	(203.72,472.61) --
	(212.30,477.86) --
	(220.88,481.80) --
	(229.46,489.82) --
	(238.04,497.94) --
	(246.62,502.53) --
	(255.20,508.10) --
	(263.78,517.98) --
	(272.36,523.55) --
	(280.94,528.79) --
	(289.52,534.22) --
	(298.10,533.76) --
	(306.68,535.43) --
	(315.26,531.67) --
	(323.84,527.31) --
	(332.42,522.81) --
	(341.00,515.11) --
	(349.58,506.34) --
	(358.16,499.06) --
	(366.74,490.57) --
	(375.32,481.01) --
	(383.90,474.65) --
	(392.48,471.50) --
	(401.06,463.52) --
	(409.64,462.18) --
	(418.22,456.66) --
	(426.80,454.47) --
	(435.38,452.02) --
	(443.96,450.86) --
	(452.54,449.28) --
	(461.12,448.63) --
	(469.70,447.61) --
	(478.28,446.68) --
	(486.86,445.61) --
	(495.44,445.89) --
	(504.02,445.15) --
	(512.60,444.87) --
	(521.18,444.55) --
	(529.76,444.50) --
	(538.34,444.36) --
	(546.92,444.13) --
	(555.50,444.22) --
	(564.08,444.08) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{49,104,142}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.64) --
	( 57.86,445.01) --
	( 66.44,444.87) --
	( 75.02,445.01) --
	( 83.60,445.57) --
	( 92.18,446.45) --
	(100.76,445.89) --
	(109.34,447.05) --
	(117.92,447.56) --
	(126.50,448.77) --
	(135.08,449.00) --
	(143.66,449.93) --
	(152.24,451.46) --
	(160.82,453.08) --
	(169.40,455.17) --
	(177.98,458.09) --
	(186.56,459.35) --
	(195.14,462.08) --
	(203.72,467.84) --
	(212.30,470.66) --
	(220.88,478.18) --
	(229.46,478.27) --
	(238.04,487.04) --
	(246.62,496.09) --
	(255.20,501.51) --
	(263.78,504.58) --
	(272.36,516.17) --
	(280.94,520.53) --
	(289.52,524.89) --
	(298.10,534.68) --
	(306.68,532.09) --
	(315.26,534.31) --
	(323.84,530.65) --
	(332.42,530.55) --
	(341.00,523.78) --
	(349.58,515.90) --
	(358.16,510.10) --
	(366.74,500.63) --
	(375.32,493.30) --
	(383.90,484.26) --
	(392.48,476.37) --
	(401.06,471.27) --
	(409.64,466.86) --
	(418.22,462.92) --
	(426.80,458.60) --
	(435.38,456.05) --
	(443.96,452.94) --
	(452.54,451.23) --
	(461.12,449.46) --
	(469.70,447.98) --
	(478.28,447.05) --
	(486.86,447.24) --
	(495.44,446.12) --
	(504.02,445.75) --
	(512.60,445.06) --
	(521.18,445.01) --
	(529.76,444.83) --
	(538.34,444.50) --
	(546.92,444.41) --
	(555.50,444.50) --
	(564.08,444.36) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{53,183,121}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.59) --
	( 57.86,444.73) --
	( 66.44,445.10) --
	( 75.02,444.73) --
	( 83.60,445.52) --
	( 92.18,446.12) --
	(100.76,445.89) --
	(109.34,446.77) --
	(117.92,447.10) --
	(126.50,448.82) --
	(135.08,448.77) --
	(143.66,449.70) --
	(152.24,450.39) --
	(160.82,451.55) --
	(169.40,455.26) --
	(177.98,456.61) --
	(186.56,458.79) --
	(195.14,461.43) --
	(203.72,465.75) --
	(212.30,469.46) --
	(220.88,473.82) --
	(229.46,480.50) --
	(238.04,485.05) --
	(246.62,492.56) --
	(255.20,499.15) --
	(263.78,503.14) --
	(272.36,513.16) --
	(280.94,518.86) --
	(289.52,524.76) --
	(298.10,531.20) --
	(306.68,529.86) --
	(315.26,535.47) --
	(323.84,533.52) --
	(332.42,528.79) --
	(341.00,526.89) --
	(349.58,516.03) --
	(358.16,513.25) --
	(366.74,505.55) --
	(375.32,492.61) --
	(383.90,488.01) --
	(392.48,477.48) --
	(401.06,473.12) --
	(409.64,467.88) --
	(418.22,465.14) --
	(426.80,459.39) --
	(435.38,456.01) --
	(443.96,455.54) --
	(452.54,452.11) --
	(461.12,450.86) --
	(469.70,449.33) --
	(478.28,447.70) --
	(486.86,447.01) --
	(495.44,446.22) --
	(504.02,446.59) --
	(512.60,445.71) --
	(521.18,444.96) --
	(529.76,445.20) --
	(538.34,444.55) --
	(546.92,444.55) --
	(555.50,444.87) --
	(564.08,444.36) --
	(572.66,444.27);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
	( 49.28,444.64) --
	( 57.86,444.96) --
	( 66.44,444.87) --
	( 75.02,445.34) --
	( 83.60,445.57) --
	( 92.18,446.08) --
	(100.76,445.89) --
	(109.34,447.56) --
	(117.92,447.84) --
	(126.50,448.58) --
	(135.08,449.05) --
	(143.66,451.00) --
	(152.24,450.72) --
	(160.82,453.36) --
	(169.40,455.91) --
	(177.98,457.91) --
	(186.56,461.25) --
	(195.14,463.80) --
	(203.72,465.98) --
	(212.30,471.92) --
	(220.88,479.43) --
	(229.46,481.98) --
	(238.04,489.17) --
	(246.62,495.99) --
	(255.20,499.61) --
	(263.78,509.82) --
	(272.36,518.08) --
	(280.94,521.00) --
	(289.52,524.71) --
	(298.10,531.99) --
	(306.68,533.57) --
	(315.26,532.32) --
	(323.84,533.48) --
	(332.42,529.30) --
	(341.00,523.09) --
	(349.58,515.66) --
	(358.16,509.59) --
	(366.74,500.40) --
	(375.32,488.94) --
	(383.90,483.75) --
	(392.48,475.81) --
	(401.06,472.34) --
	(409.64,465.14) --
	(418.22,461.20) --
	(426.80,457.49) --
	(435.38,454.85) --
	(443.96,453.22) --
	(452.54,450.44) --
	(461.12,448.54) --
	(469.70,447.89) --
	(478.28,446.96) --
	(486.86,447.33) --
	(495.44,445.71) --
	(504.02,444.92) --
	(512.60,445.43) --
	(521.18,445.10) --
	(529.76,444.83) --
	(538.34,444.87) --
	(546.92,444.32) --
	(555.50,444.27) --
	(564.08,443.99) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
	( 49.28,444.73) --
	( 57.86,444.83) --
	( 66.44,445.29) --
	( 75.02,445.10) --
	( 83.60,445.43) --
	( 92.18,446.08) --
	(100.76,446.54) --
	(109.34,446.82) --
	(117.92,448.26) --
	(126.50,448.63) --
	(135.08,449.42) --
	(143.66,450.44) --
	(152.24,451.92) --
	(160.82,454.38) --
	(169.40,456.28) --
	(177.98,457.21) --
	(186.56,461.43) --
	(195.14,465.10) --
	(203.72,468.62) --
	(212.30,472.06) --
	(220.88,476.60) --
	(229.46,482.68) --
	(238.04,491.35) --
	(246.62,496.64) --
	(255.20,505.78) --
	(263.78,511.49) --
	(272.36,516.17) --
	(280.94,525.50) --
	(289.52,528.14) --
	(298.10,530.69) --
	(306.68,535.15) --
	(315.26,535.66) --
	(323.84,530.42) --
	(332.42,526.05) --
	(341.00,520.02) --
	(349.58,514.46) --
	(358.16,504.16) --
	(366.74,498.50) --
	(375.32,490.84) --
	(383.90,481.06) --
	(392.48,474.24) --
	(401.06,468.35) --
	(409.64,466.49) --
	(418.22,461.11) --
	(426.80,456.70) --
	(435.38,454.34) --
	(443.96,452.67) --
	(452.54,451.92) --
	(461.12,449.74) --
	(469.70,448.21) --
	(478.28,447.28) --
	(486.86,447.01) --
	(495.44,445.71) --
	(504.02,445.52) --
	(512.60,445.20) --
	(521.18,445.34) --
	(529.76,444.55) --
	(538.34,444.41) --
	(546.92,444.18) --
	(555.50,444.13) --
	(564.08,444.27) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{49,104,142}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
	( 49.28,444.78) --
	( 57.86,445.24) --
	( 66.44,445.10) --
	( 75.02,445.48) --
	( 83.60,445.85) --
	( 92.18,446.50) --
	(100.76,446.82) --
	(109.34,447.47) --
	(117.92,448.12) --
	(126.50,449.51) --
	(135.08,450.53) --
	(143.66,450.95) --
	(152.24,454.01) --
	(160.82,454.89) --
	(169.40,458.70) --
	(177.98,459.67) --
	(186.56,462.45) --
	(195.14,467.09) --
	(203.72,471.59) --
	(212.30,476.37) --
	(220.88,480.13) --
	(229.46,488.57) --
	(238.04,494.65) --
	(246.62,501.47) --
	(255.20,509.54) --
	(263.78,516.68) --
	(272.36,522.34) --
	(280.94,526.33) --
	(289.52,531.20) --
	(298.10,533.29) --
	(306.68,535.47) --
	(315.26,532.78) --
	(323.84,529.53) --
	(332.42,521.74) --
	(341.00,514.69) --
	(349.58,505.41) --
	(358.16,500.03) --
	(366.74,492.28) --
	(375.32,483.33) --
	(383.90,477.99) --
	(392.48,471.45) --
	(401.06,466.40) --
	(409.64,462.55) --
	(418.22,458.42) --
	(426.80,455.40) --
	(435.38,453.83) --
	(443.96,451.55) --
	(452.54,450.49) --
	(461.12,448.30) --
	(469.70,448.07) --
	(478.28,447.38) --
	(486.86,446.45) --
	(495.44,445.34) --
	(504.02,445.43) --
	(512.60,445.29) --
	(521.18,445.06) --
	(529.76,444.50) --
	(538.34,444.50) --
	(546.92,444.36) --
	(555.50,444.22) --
	(564.08,444.18) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{53,183,121}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
	( 49.28,444.64) --
	( 57.86,445.24) --
	( 66.44,445.06) --
	( 75.02,445.29) --
	( 83.60,445.80) --
	( 92.18,446.31) --
	(100.76,446.91) --
	(109.34,447.52) --
	(117.92,447.52) --
	(126.50,448.86) --
	(135.08,450.21) --
	(143.66,450.49) --
	(152.24,452.94) --
	(160.82,454.94) --
	(169.40,456.66) --
	(177.98,460.00) --
	(186.56,462.04) --
	(195.14,466.44) --
	(203.72,469.55) --
	(212.30,474.19) --
	(220.88,479.43) --
	(229.46,486.34) --
	(238.04,492.84) --
	(246.62,498.92) --
	(255.20,508.70) --
	(263.78,512.79) --
	(272.36,520.49) --
	(280.94,525.27) --
	(289.52,529.02) --
	(298.10,534.27) --
	(306.68,534.08) --
	(315.26,534.27) --
	(323.84,526.94) --
	(332.42,525.96) --
	(341.00,517.29) --
	(349.58,511.35) --
	(358.16,501.61) --
	(366.74,495.30) --
	(375.32,486.62) --
	(383.90,478.69) --
	(392.48,470.85) --
	(401.06,469.37) --
	(409.64,463.71) --
	(418.22,457.54) --
	(426.80,456.42) --
	(435.38,453.96) --
	(443.96,452.53) --
	(452.54,449.79) --
	(461.12,449.84) --
	(469.70,447.61) --
	(478.28,447.89) --
	(486.86,446.45) --
	(495.44,445.75) --
	(504.02,445.48) --
	(512.60,445.29) --
	(521.18,444.92) --
	(529.76,444.50) --
	(538.34,444.45) --
	(546.92,444.27) --
	(555.50,444.22) --
	(564.08,444.22) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,444.96) --
	( 57.86,445.34) --
	( 66.44,444.78) --
	( 75.02,445.94) --
	( 83.60,446.54) --
	( 92.18,446.50) --
	(100.76,447.24) --
	(109.34,447.42) --
	(117.92,448.49) --
	(126.50,449.93) --
	(135.08,450.44) --
	(143.66,452.39) --
	(152.24,454.24) --
	(160.82,456.93) --
	(169.40,458.33) --
	(177.98,461.90) --
	(186.56,465.38) --
	(195.14,468.21) --
	(203.72,472.01) --
	(212.30,478.83) --
	(220.88,484.12) --
	(229.46,491.26) --
	(238.04,498.04) --
	(246.62,505.04) --
	(255.20,513.39) --
	(263.78,519.70) --
	(272.36,523.69) --
	(280.94,529.86) --
	(289.52,531.90) --
	(298.10,535.94) --
	(306.68,537.28) --
	(315.26,529.30) --
	(323.84,529.12) --
	(332.42,519.28) --
	(341.00,513.67) --
	(349.58,502.81) --
	(358.16,494.83) --
	(366.74,488.15) --
	(375.32,479.99) --
	(383.90,476.05) --
	(392.48,467.42) --
	(401.06,465.38) --
	(409.64,459.58) --
	(418.22,455.91) --
	(426.80,454.94) --
	(435.38,452.80) --
	(443.96,451.41) --
	(452.54,449.46) --
	(461.12,448.21) --
	(469.70,447.33) --
	(478.28,446.82) --
	(486.86,446.08) --
	(495.44,445.71) --
	(504.02,444.92) --
	(512.60,444.50) --
	(521.18,444.78) --
	(529.76,444.59) --
	(538.34,444.69) --
	(546.92,444.36) --
	(555.50,444.36) --
	(564.08,444.04) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.18) --
	( 49.28,444.96) --
	( 57.86,445.01) --
	( 66.44,444.96) --
	( 75.02,445.80) --
	( 83.60,445.57) --
	( 92.18,445.80) --
	(100.76,446.59) --
	(109.34,447.38) --
	(117.92,448.35) --
	(126.50,448.63) --
	(135.08,448.82) --
	(143.66,451.55) --
	(152.24,451.88) --
	(160.82,453.64) --
	(169.40,455.54) --
	(177.98,459.11) --
	(186.56,460.92) --
	(195.14,465.42) --
	(203.72,470.99) --
	(212.30,473.54) --
	(220.88,477.44) --
	(229.46,483.65) --
	(238.04,494.00) --
	(246.62,500.17) --
	(255.20,503.23) --
	(263.78,512.09) --
	(272.36,523.46) --
	(280.94,526.15) --
	(289.52,535.01) --
	(298.10,532.64) --
	(306.68,532.73) --
	(315.26,540.06) --
	(323.84,533.85) --
	(332.42,522.81) --
	(341.00,518.35) --
	(349.58,512.00) --
	(358.16,502.16) --
	(366.74,495.99) --
	(375.32,486.62) --
	(383.90,477.76) --
	(392.48,472.98) --
	(401.06,470.11) --
	(409.64,463.15) --
	(418.22,457.17) --
	(426.80,457.54) --
	(435.38,454.01) --
	(443.96,451.13) --
	(452.54,449.88) --
	(461.12,448.49) --
	(469.70,447.42) --
	(478.28,446.96) --
	(486.86,446.59) --
	(495.44,445.61) --
	(504.02,445.52) --
	(512.60,444.87) --
	(521.18,444.55) --
	(529.76,444.64) --
	(538.34,444.59) --
	(546.92,444.41) --
	(555.50,444.50) --
	(564.08,444.22) --
	(572.66,444.32);
\definecolor{drawColor}{RGB}{49,104,142}
